A survey of HTTP caching options on the open Web

### 2015-01-13 sanity/paper1.tex
All references
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@967 43ef1190-90fd-4dd7-a769-d0121f02b80e
LOV ref
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@968 43ef1190-90fd-4dd7-a769-d0121f02b80e

\title{A survey of HTTP caching options on the open Web}
\author{Kjetil Kjernsmo\inst{1}}
\institute{Department of Informatics,
Postboks 1080 Blindern,
N-0316 Oslo, Norway \email{kjetil@kjernsmo.net}

@@

To compile a list of Web ontologies, we first queried the Linked Open
Vocabularies \todo{ref} SPARQL endpoint to retrieve all registered
ontologies. Then, we took the full list of URIs registered with
prefix.cc. The assumption that they all identify an ontology is
clearly false, as we found that for example Tim Berners-Lee's FOAF
profile has a registered URI, but it is unlikely to introduce
significant bias.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{webarch,data,rfc,hypermedia,dynamicity}

\begin{appendices}

@@

Finally, if the LOV SPARQL endpoint used a URI for the vocabulary that
was different from the namespace URI (after a normalization step),
another request would be made to record the selected HTTP headers from
that as well.\todo{say how many requests failed? It was a lot}
\end{appendices}

>>>>

\title{A survey of HTTP caching options on the open Web}
\author{Kjetil Kjernsmo\inst{1}}
\institute{Department of Informatics,
Postboks 1080 Blindern,
N-0316 Oslo, Norway \email{kjetil@kjernsmo.net}}

@@

To compile a list of Web ontologies, we first queried the Linked Open
Vocabularies (LOV) \cite{doi:10.1108/LHT-03-2013-0027} SPARQL endpoint
to retrieve all registered ontologies. Then, we took the full list of
URIs registered with prefix.cc. The assumption that they all identify
an ontology is clearly false, as we found that for example Tim
Berners-Lee's FOAF profile has a registered URI, but it is unlikely to
introduce significant bias.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{webarch,data,rfc,hypermedia,dynamicity,stat1,specs}

\begin{subappendices}
\renewcommand{\thesection}{\Alph{section}}%

@@

Finally, if the LOV SPARQL endpoint used a URI for the vocabulary that
was different from the namespace URI (after a normalization step),
another request would be made to record the selected HTTP headers from
that as well.\todo{say how many requests failed? It was a lot}
\end{subappendices}
